Dependent Object Types

### 2012-08-29 doc/candidacy/report.tex
beg of tribe paper

>>>>

In~\cite{tribe}, Clarke et al. present a calculus for virtual
classes. Virtual classes allows {\it families} of classes to be
inherited, rather than just single classes. Classes are lexically
nested inside other classes. When a class is inherited, its nested
inner classes are inherited along with its methods and fields. {\it
  Further binding} enables the nested classes to be further extended.

Though Scala doesn't have virtual classes, its abstract types enables
it to emulate some (but not all) of the benefits of virtual classes as
presented in the Tribe calculus.
